Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

  # Histogram sebaran awal
  p1 <- ggplot(data = df_awal, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 1) +
    geom_density(aes(y = after_stat(count)), fill = color, alpha = 0.4) +
    labs(title = paste0(title, "\nSebaran Awal")) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )

  # Histogram rataan sampel
  p2 <- ggplot(data = df_rataan, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 1) +
    geom_density(aes(y = after_stat(count)), fill = color, alpha = 0.4) +
    labs(title = paste0(title, "\nRata-rata Sampel")) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )

>>>>

  # Histogram sebaran awal
  p1 <- ggplot(data = df_awal, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 1) +
    geom_density(aes(y = ..density..), adjust = 3, fill = color, alpha = 0.4) + # Adjust density
    labs(title = paste0(title, "\nSebaran Awal")) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )

  # Histogram rataan sampel
  p2 <- ggplot(data = df_rataan, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 1) +
    geom_density(aes(y = ..density..), adjust = 3, fill = color, alpha = 0.4) + # Adjust density
    labs(title = paste0(title, "\nRata-rata Sampel")) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )
